---
title: "ASSIGNMENT 5"
author: "Kiran Komati"
date: '2021-04-30'
output:
  pdf_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = 'C:/Users/kiran/dsc520')
```
## Load the `data/r4ds/heights.csv` to heights_df

```{r echo=TRUE}
heights_df <- read.csv("data/r4ds/heights.csv")
```

## Using `cor()` compute correlation coefficients for
### height vs. earn

```{r include=TRUE,echo=TRUE}
cor(heights_df$height,heights_df$earn,use="everything",method="pearson")
```

### age vs. earn 

```{r include=TRUE,echo=TRUE}
cor(heights_df$age,heights_df$earn,use="everything",method="pearson")
```

### ed vs. earn

```{r include=TRUE,echo=TRUE}
cor(heights_df$ed,heights_df$earn,use="everything",method="pearson") 
```


## Spurious correlation
## The following is data on US spending on science, space, and technology in millions of today's dollars and Suicides by hanging strangulation and suffocation for the years 1999 to 2009
## Compute the correlation between these variables


```{r include=TRUE,echo=TRUE}
tech_spending <- c(18079, 18594, 19753, 20734, 20831, 23029, 23597, 23584, 25525, 27731, 29449)
suicides <- c(5427, 5688, 6198, 6462, 6635, 7336, 7248, 7491, 8161, 8578, 9000)
cor(tech_spending,suicides,use="everything",method="pearson") 
```