---
title: "assignment 06"
author: "Kiran Komati"
date: "5/16/2021"
output:
  pdf_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = 'C:/Users/kiran/dsc520')
```

## Load the `data/r4ds/heights.csv` to heights_df

```{r echo=TRUE}
heights_df <- read.csv("data/r4ds/heights.csv")
```

## Load the ggplot2 library
```{r echo=TRUE}
library(ggplot2)
```

## Fit a linear model using the `age` variable as the predictor and `earn` as the outcome

```{r echo=TRUE}
age_lm <-  lm(earn ~ age,data = heights_df)
```

## View the summary of your model

```{r echo=TRUE}
summary(age_lm)
```

## Creating predictions using `predict()`

```{r echo=TRUE}
age_predict_df <- data.frame(earn = predict(age_lm, newdata = heights_df), age=heights_df$age)
```
## Plot the predictions against the original data
```{r echo=TRUE}
ggplot(data = heights_df, aes(y = earn, x = age)) +
  geom_point(color='blue') +
  geom_line(color='red',data = age_predict_df, aes(y=earn, x=age))
```

## Calculate Mean
```{r echo=TRUE}
mean_earn <- mean(heights_df$earn)
```

## Corrected Sum of Squares Total
```{r echo=TRUE}
sst <- sum((mean_earn - heights_df$earn)^2)
```

## Corrected Sum of Squares for Model
```{r echo=TRUE}
ssm <- sum((mean_earn - age_predict_df$earn)^2)
```
## Residuals
```{r echo=TRUE}
residuals <- heights_df$earn - age_predict_df$earn
```
## Sum of Squares for Error
```{r echo=TRUE}
sse <- sum(residuals^2)
```

## R Squared 
```{r echo=TRUE}
r_squared <- ssm/sst
```
## Number of observations
```{r echo=TRUE}
n <- nrow(heights_df)
```
## Number of regression paramaters
```{r echo=TRUE}
p <- 2
```
## Corrected Degrees of Freedom for Model
```{r echo=TRUE}
dfm <- p-1
```
## Degrees of Freedom for Error
```{r echo=TRUE}
dfe <- n-p
```
## Corrected Degrees of Freedom Total:   DFT = n - 1
```{r echo=TRUE}
dft <- n-1
```

## Mean of Squares for Model:   MSM = SSM / DFM
```{r echo=TRUE}
msm <- ssm/dfm
```
## Mean of Squares for Error:   MSE = SSE / DFE
```{r echo=TRUE}
mse <- sse/dfe
```

## Mean of Squares Total:   MST = SST / DFT
```{r echo=TRUE}
mst <- sst/dft

```
## F Statistic
```{r echo=TRUE}
f_score <- msm/mse
```

## Adjusted R Squared R2 = 1 - (1 - R2)(n - 1) / (n - p)
```{r echo=TRUE}
adjusted_r_squared <- 1 - (1 - r_squared)*(n - 1) / (n - p)
```